\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-15 paper/mswp2012-proposal.tex
updated Glossar and moved Footnote to Bib

Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays. These people don’t only look bad. They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.  \\

@@

 \begin{description}
  \item[MSWP] Management von Software Projekten
  \item[WP] Work Package
 \end{description}

>>>>

Studies \citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. These people don’t only look bad. They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.  \\

@@

 \begin{description}
  \item[MSWP] Management von Software Projekten
  \item[WP] Work Package
  \item[OECD] Organisation for Economic Co-operation and Development
  \item[RKI] Robert Koch Institut
 \end{description}
